Revisiting Multi-Domain Machine Translation

### 2020-04-09 2020/coling2020/multidomain.tex
more refs, notes on a theoretical part

\subsection{MDMT: a tentative definition}
Informally, a multi-domain system should be able to accurately translate heterogeneous sources of data. This loose definition correspond to several practical situations:
\begin{itemize}
\item the more common situation is when both train and test documents (or sentences) are domain-tagged, where each domain corresponds to a specific source of data, and differ from the other sources in terms of textual genre, thematic content \cite{Zhang16topicinformed}, register, style \cite{Niu18multitask}, etc. It is usually assumed that the set of test domains is the same as the set of training domains -- when this is not the case, we would have zero-shot domain adaptation, similar to what is studied in multilingual MT \cite{Firat16multiway,Ha16towards,Johnson17google,Platanios18contextual}. This is the more general setting, already proposed in \cite{Dredze09multidomain}.\fyTodo{do we need a name: such as supervised MDMT ? and mostly supervised MDMT for the second case ?}

@@

We experiment with translation from English into French and use data initially originating from 6~domains, corresponding to texts from the following data sources: the UFAL Medical corpus V1.0 (\domain{MED})\footnote{\url{https://ufal.mff.cuni.cz/ufal_medical_corpus}}, the European Central Bank corpus (\domain{Bank}) \cite{Tiedemann12parallel}; The JRC-Acquis Communautaire corpus (LAW) \cite{Steinberger06acquis}, documentations for KDE, Ubuntu, GNOME and PHP from Opus collection \cite{Tiedemann09news}, collectively merged in a \domain{IT}-Domain, Ted Talks (\domain{Talks}) \cite{Cettolo12wit}, and the Koran (\domain{Rel}). Complementary experiments also use v12 of the News Commentary corpus (\domain{News}). Corpus statistics in Table~\ref{tab:Corpora}.  Most corpora are variable from the Opus web site.\footnote{\url{http://opus.nlpl.eu}} These corpora were deduplicated and tokenized with in-house tools. To reduce the number of types and build open-vocabulary systems, we use Byte-Pair Encodings \cite{Sennrich16BPE} with 30,000 merge operations on a corpus containing all sentences in both languages.%

@@

\begin{table}[h]
  \centering
  \begin{tabular}{ |lllllll|} %*{4}{|r|}}
    \hline
    %\multicolumn{4}{|l|}{Vocab size - En: 30,165, Fr: 30,398}\\
    \domain{Med} & \domain{Law} & \domain{Bank} & \domain{IT} & \domain{Talk} & \domain{Rel} & \domain{News} \\
    \hline
    2609 (0.68) & 190 (0.05)  & 501 (0.13) & 270 (0.07) & 160 (0.04) & 130 (0.03) & 260 (0) \\
    \hline
  \end{tabular}
\caption{Corpora statistics: number of parallel lines ($\times 10^3$) and proportion in the basic domain mix (which excludes the \domain{News} domain).}
\label{tab:Corpora}
\end{table}

We measure the distance between domains using the $\mathcal{H}$-Divergence introduced in \cite{Ben-David09atheory}, which relates domain similarity to the test error of a domain discriminator: the larger the error, the closer the domains. Formally, given test sets of size $m$ for domains $A$ and $B$, and $h(x)$ a trained domain predictor, $\mathcal{H}(A,B)$ is computed as:
$$
\mathcal{H}(A,B) = 2(1 - [\frac{1}{m} \sum_{x:h(x) = B} \mathbb{I}( x \in A) + \frac{1}{m} \sum_{x: h(x) = A} \mathbb{I}(x \in B)]),
$$
where $\mathbb{I}$ is the indicator function. The  domain discriminator is a multilayer perceptron independently trained for each pair of domains with sentence representations derived via mean pooling from the source side representation of our generic Transformer model. The hidden layer has dimension XXX, and the network is trained on balanced sets of YYY instances for ZZZ epochs.\fyTodo{Inform the classifier details}.

@@

\section{Results and discussion \label{sec:results}}
\subsection{Performance of MDMT systems \label{ssec:rawperformance}}
In this section, we discuss the raw performance of MDMT systems trained and tested on $6$~domains. Results are in Table~\ref{tab:performance}. As expected, balancing data in the generic setting makes a great difference (the unweighted average is 2~BLEU points \jcDone{BP?} better, notably owing to the much better results for \domain{REL}). As explained above, this setting should be the baseline when the test distribution is assumed to be balanced across domains. As all other systems are trained with an unbalanced data distribution, use the weighted average to perform global comparisons.

Fine-tuning each domain separately provides us with better baselines, significantly outperforming \system{generic} for all domains. A complete fine-tuning, which updates all parameters, proves more effective than only adapting a subpart of the network - a result that could be due to lack of tuning the capacity of the adapter module. \fyDone{Add 2 averages ?}\fyTodo{Significance testing wrt Mix Generic, Full Fine-tuned, for each domain}
A  first group of MDMTs use an extra domain feature, at the sentence or at the word level: among these, having the domain tag on the source is better than on the target, and very comparable to repeating the tag for every source word. All (except \system{DM} and \system{ADM}) improve over the generic baseline (for most domains), matching requirement [P1-LAB], but yield weaker results than fine tuning. As expected, the gap with fine-tuning remains large for an ``isolated'' domain such as \domain{rel}, the best contender being overall \system{MDL Res}, which approximately halves this gap as compared to \system{Mixed-Nat}.
\fyTodo{More comments when we have all the results}
The use of an decidated adaptation component in each of the transformer layer proves an even better strategy and closes the gap with fine-tuning for half of the domains: the use of a gating mechanism yielding a clear improvement over the board. The effect of the adaptation layer is especially significant for the smaller domains (\domain{bank}, \domain{IT} and \domain{rel}) for which unplugging this layer causes dramatic performance drops.

@@

\begin{table}
  \centering
  \fyTodo{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}|r|} \hline
%     &&&&&& \\
    Model / Domain & \multicolumn{1}{c|}{\domain{med}} & \multicolumn{1}{c|}{\domain{law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talks}} & \multicolumn{1}{c|}{\domain{it}} & \multicolumn{1}{c|}{\domain{rel}} & \multicolumn{1}{c|}{\domain{wAVG}} & \multicolumn{1}{c|}{\domain{AVG}} & \multicolumn{1}{|c|}{\domain{News}} \\ \hline
    \system{Mixed-Nat}  & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 &\\
    \system{Mixed-Bal}   &  35.3 & 54.1 & 52.5 & 31.9 & 44.9 & 89.5 & 40.3  & 51.4 &\\
    \system{FT-Full}       & 37.7 & 59.2 & 54.5 & 34.0 & 46.8 & 90.8   & 42.8 & 53.8 &\\
   \system{FT-Block}     & 37.3 & 57.9 & 53.9 & 33.8 & 46.7 & 90.2    & 42.3 & 53.3 &\\ \hline

 %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn

    \system{DC-Tag}   & 38.1 & 55.3 & 49.9   & 33.2 & 43.5 & 80.5 &41.7 & 50.1     &\\
    \system{DC-Feat}  & 37.3   & 54.9 & 49.5   & 32.9 & 43.6 & 79.9 &41.4 & 49.9   & \\
    \system{TTM}        & 37.7 & 54.8 & 49.7 & 33.4 & 43.8 & 80.0 &41.1 & 49.7       & \\
    \system{LDC-Tag} &&&&& &&&\\
    \system{DM}             & 36.5 & 52.4  & 47.7& 32.1 & 41.0 & 70.4 & 39.7 & 46.7 & \\
    \system{ADM}           & 37.1 & 53.8  & 48.9 &32.8 & 42.3 & 78.5 & 40.7 & 48.9 & \\
    \system{WDCMT}      & & & & & & & & \\
    \system{MDL Res}     & 37.9 & 56.0  & 51.2   & 33.5   &  44.4  & 88.3 & 42.1 & 51.9       &\\
    \system{MDL Res} (gen)           & 37.7 & 51.0 & 34.0 & 30.4 & 34.2 & 15.2 & 36.4 & 33.7&\\
%    \system{MDL Gated} & 37.7 & 56.5 & 53.2 & 34.1 & 44.6 & 90.7 & 42.3 & 53.3&\\
     \hline
  \end{tabular}
  \caption{Translation performance of various MDMT systems. We report the BLEU score for each domain, as well as domain-weighted (wAVG) and unweighted (AVG) averages. (*) denotes significant improvements with respect to the \system{Mix-Nat} system. Scores for the \domain{News} domain correspond to the out-of-domain scenario (see ~\ref{ssec:redomains}).  }
  \label{tab:performance}
\end{table}
\fyTodo{Fill the table with all results, including a comparison with *RNNs* for wcmd}
\ftTodo{A new column for the News domain with predicted domains (except for the generic case).}

@@

\fyTodo{Instert table, significancy testing against full learning condition, for each domain}

@@

In \cite{Britz17mixing}, several methods are considered which aim to ensure that domain information is actually used in a mix-domain system. Three alternatives are considered, using either domain classification (or domain normalization, via adversarial training) on source or target representations. There is no clear winner in either of their three language pairs considered, which only distinguish a limited number of domains. The same basic techniques are simultaneously at play in \cite{Zeng18multidomain,Su19exploring}: in this approach, the upper layers of the MT aimed to sort out domain specific information on the one hand, and domain-agnostic information on the other hand, using auxiliary classification tasks, hoping that the domain-specific part will capture specific peculiarities of a domain, while the domain-agnostic part will be useful across the board. These two sets of representations are then input to a conventional attentional sequence-to -sequence models in \cite{Zeng18multidomain}, and with Transformers in \cite{Su19exploring}.

@@

>>>>

\subsection{MDMT: a tentative definition}
Informally, a multi-domain system should be able to accurately translate heterogeneous sources of data. This loose definition correspond to several practical situations:
\begin{itemize}
\item the more common situation is when both train and test documents (or sentences) are domain-tagged, where each domain corresponds to a specific source of data, and differ from the other sources in terms of textual genre, thematic content \cite{Zhang16topicinformed}, register, style \cite{Niu18multitask}, etc. It is usually assumed that the set of test domains is the same as the set of training domains -- when this is not the case, we would have zero-shot domain adaptation, similar to what is studied in multilingual MT \cite{Firat16multiway,Ha16towards,Johnson17google,Platanios18contextual}. This is the more general setting, already proposed in \cite{Dredze09multidomain}.\fyTodo{do we need a name here: such as supervised MDMT ? and mostly supervised MDMT for the second case ?}

@@

We experiment with translation from English into French and use data initially originating from 6~domains, corresponding to texts from the following data sources: the UFAL Medical corpus V1.0 (\domain{med})\footnote{\url{https://ufal.mff.cuni.cz/ufal_medical_corpus}}, the European Central Bank corpus (\domain{bank}) \cite{Tiedemann12parallel}; The JRC-Acquis Communautaire corpus (\domain{law}) \cite{Steinberger06acquis}, documentations for KDE, Ubuntu, GNOME and PHP from Opus collection \cite{Tiedemann09news}, collectively merged in a \domain{it}-domain, Ted Talks (\domain{talk}) \cite{Cettolo12wit}, and the Koran (\domain{rel}). Complementary experiments also use v12 of the News Commentary corpus (\domain{news}). Corpus statistics in Table~\ref{tab:Corpora}.  Most corpora are variable from the Opus web site.\footnote{\url{http://opus.nlpl.eu}} These corpora were deduplicated and tokenized with in-house tools. To reduce the number of types and build open-vocabulary systems, we use Byte-Pair Encodings \cite{Sennrich16BPE} with 30,000 merge operations on a corpus containing all sentences in both languages.%

@@

\begin{table}[h]
  \centering
  \begin{tabular}{ |lllllll|} %*{4}{|r|}}
    \hline
    %\multicolumn{4}{|l|}{Vocab size - En: 30,165, Fr: 30,398}\\
    \domain{med} & \domain{law} & \domain{bank} & \domain{it} & \domain{talk} & \domain{rel} & \domain{news} \\
    \hline
    2609 (0.68) & 190 (0.05)  & 501 (0.13) & 270 (0.07) & 160 (0.04) & 130 (0.03) & 260 (0) \\
    \hline
  \end{tabular}
\caption{Corpora statistics: number of parallel lines ($\times 10^3$) and proportion in the basic domain mix (which excludes the \domain{news} domain).}
\label{tab:Corpora}
\end{table}

We measure the distance between domains using the $\mathcal{H}$-Divergence introduced in \cite{Ben-David09atheory}, which relates domain similarity to the test error of a domain discriminator: the larger the error, the closer the domains. Formally, given test sets of size $m$ for domains $A$ and $B$, and $h(x)$ a trained domain predictor, $\mathcal{H}(A,B)$ is computed as:
$$
\mathcal{H}(A,B) = 2(1 - [\frac{1}{m} \sum_{x:h(x) = B} \mathbb{I}( x \in A) + \frac{1}{m} \sum_{x: h(x) = A} \mathbb{I}(x \in B)]),
$$
where $\mathbb{I}$ is the indicator function. Our domain discriminator is a multilayer perceptron independently trained for each pair of domains with sentence representations derived via mean pooling from the source side representation of our generic Transformer model. The hidden layer has dimension XXX, and the network is trained on balanced sets of YYY instances for ZZZ epochs.\fyTodo{Inform the classifier details}.

@@

\section{Results and discussion \label{sec:results}}
\subsection{Performance of MDMT systems \label{ssec:rawperformance}}
In this section, we discuss the raw performance of MDMT systems trained and tested on $6$~domains. Results are in Table~\ref{tab:performance}. As expected, balancing data in the generic setting makes a great difference (the unweighted average is 2~BLEU points \jcDone{BP?} better, notably owing to the much better results for \domain{rel}). As explained above, this setting should be the baseline when the test distribution is assumed to be balanced across domains. As all other systems are trained with an unbalanced data distribution, use the weighted average to perform global comparisons.

Fine-tuning each domain separately provides us with better baselines, significantly outperforming \system{generic} for all domains. A complete fine-tuning, which updates all parameters, proves more effective than only adapting a subpart of the network - a result that could be due to lack of tuning the capacity of the adapter module. \fyDone{Add 2 averages ?}\fyTodo{Significance testing wrt Mix Generic, Full Fine-tuned, for each domain}
A  first group of MDMTs use an extra domain feature, at the sentence or at the word level: among these, having the domain tag on the source is better than on the target, and very comparable to repeating the tag for every source word. All (except \system{DM} and \system{ADM}) improve over the generic baseline (for most domains), matching requirement [P1-LAB], but yield weaker results than fine tuning. As expected, the gap with fine-tuning remains large for an ``isolated'' domain such as \domain{rel}, the best contender being overall \system{MDL Res}, which approximately halves this gap as compared to \system{Mixed-Nat}.
\fyTodo{More comments when we have all the results}
The use of an decidated adaptation component in each of the transformer layer proves an even better strategy and closes the gap with fine-tuning for half of the domains: the use of a gating mechanism yielding a clear improvement over the board. The effect of the adaptation layer is especially significant for the smaller domains (\domain{bank}, \domain{it} and \domain{rel}) for which unplugging this layer causes dramatic performance drops.

@@

\begin{table*}
  \centering
  \fyDone{Fix column size}
  \begin{tabular}{|p{3cm}|*{8}{r|}|r|} \hline
%     &&&&&& \\
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c||}{\domain{avg}} & \multicolumn{1}{c|}{\domain{news}} \\ \hline
    \system{Mixed-Nat}  & 37.3 & 54.6 & 50.1 & 33.5 & 43.2 & 77.5  & 41.1  & 49.4 &\\
    \system{Mixed-Bal}   &  35.3 & 54.1 & 52.5 & 31.9 & 44.9 & 89.5 & 40.3  & 51.4 &\\
    \system{FT-Full}       & 37.7 & 59.2 & 54.5 & 34.0 & 46.8 & 90.8   & 42.8 & 53.8 &\\
   \system{FT-Block}     & 37.3 & 57.9 & 53.9 & 33.8 & 46.7 & 90.2    & 42.3 & 53.3 &\\ \hline
 %   Full-finetuned on extended in-domain corpora (news) & && 33.96&&& & &\\nn
    \system{DC-Tag}       & 38.1 & 55.3 & 49.9   & 33.2 & 43.5 & 80.5 &41.7 & 50.1     &\\
    \system{DC-Feat}      & 37.3  & 54.9 & 49.5   & 32.9 & 43.6 & 79.9 &41.4 & 49.9   & \\
    \system{TTM}            & 37.7 & 54.8 & 49.7 & 33.4 & 43.8 & 80.0 &41.1 & 49.7       & \\
    \system{LDC-Tag}     & 37   & 54.7 & 49.9 & 33.9 & 43.6 & 79.9 & & & \\ 
    \system{DM}             & 36.5 & 52.4  & 47.7& 32.1 & 41.0 & 70.4 & 39.7 & 46.7 & \\
    \system{ADM}           & 37.1 & 53.8  & 48.9 &32.8 & 42.3 & 78.5 & 40.7 & 48.9 & \\
    \system{WDCMT}       & & & & & & & & &\\
    \system{MDL Res}     & 37.9 & 56.0  & 51.2   & 33.5   &  44.4  & 88.3 & 42.1 & 51.9       &\\
    \system{MDL Res} (gen)           & 37.7 & 51.0 & 34.0 & 30.4 & 34.2 & 15.2 & 36.4 & 33.7&\\
%    \system{MDL Gated} & 37.7 & 56.5 & 53.2 & 34.1 & 44.6 & 90.7 & 42.3 & 53.3&\\
     \hline
  \end{tabular}
  \caption{Translation performance of various MDMT systems. We report the BLEU score for each domain, as well as domain-weighted (w\domain{avg}) and unweighted (\domain{avg}) averages. (*) denotes significant improvements with respect to the \system{Mix-Nat} system. Scores for the \domain{news} domain correspond to the out-of-domain scenario (see section~\ref{ssec:performance}).}
  \label{tab:performance}
\end{table*}
\fyTodo{Fill the table with all results, including a comparison with *RNNs* for wcmd}
\fyTodo{A new column for the News domain with predicted domains (except for the generic case).}

@@

\begin{table*}
  \begin{tabular}{|p{3cm}|*{9}{r|}} \hline
    Model / Domain & \multicolumn{1}{c|}{\domain{ med}} & \multicolumn{1}{c|}{\domain{ law}} & \multicolumn{1}{c|}{\domain{bank}} & \multicolumn{1}{c|}{\domain{talk}} & \multicolumn{1}{c|}{\domain{ it }} & \multicolumn{1}{c|}{\domain{ rel}} & \multicolumn{1}{c|}{\domain{news}} & \multicolumn{1}{c|}{w\domain{avg}} & \multicolumn{1}{c||}{\domain{avg}} \\ \hline

    \system{Mixed-Nat}  & 37.3  & 54.6   & 50.1   & 33.5  & 43.2  & 77.5  & & 41.1 & 49.4 \\
    \system{FT-Full}       & 37.7  & 59.2   & 54.5   & 34.0  & 46.8  & 90.8  & & 42.8 & 53.8 \\ \hline\hline
     \system{DC-Feat}     & 37.4 & 54.9   & 50.0    & 34.7  &  43.9  & 79.6 & 28.9 \\
                                    & 36.9 & 53.7   & 49.1    & 33.7  &  42.8  & 74.1 & 28.9 &\\
    \system{DC-Tag}      &  37.7 & 54.5   & 49.9    &  34.8 &  43.9  & 78.8 & 29.5 \\
                                   & 38.0  & 54.0   & 48.8    & 33.5  &  42.7  &73.2  & 28.3& \\
    \system{TTM}           &  37.3 & 54.4   & 49.6    & 33.8  &  42.9  &78.1  & 29.1 \\
                                   & 36.8  & 53.4   & 47.9    & 32.4  &  42.5  &72.8  & 28.4& \\
    \system{LDC-Tag}    & 37.0   & 54.6  & 49.6    & 34.3  &  43.0  &77.0  & 28.7 \\
    continual                 &&&&&& \\
    \system{DM}            &36.0 &51.3&46.8&31.8&39.8&65.7&27.0 \\
                                  &36.5&51.6&47.3&31.7&40.3&65.7&25.8& \\
    \system{ADM}          &36.6&54.2&49.1&32.9&42.1&75.7&28.7 \\
                                  &  36.9 &53.5&48.3&32.7&41.7&70.7&26.8& \\
    \system{WDCMT}     &34.8  &51.8&47.8&30.7&37.3&49.3&25.9 \\
    continual                 &&&&&&&& \\
    \system{MDL-Res}    &37.7   & 55.6   & 51.1   & 34.4  & 44.5  & 87.5  & 29.1 & & \\
     continual                &&&&&&&& \\
     \hline
  \end{tabular}
  \caption{Ability to handle new a domain: BLEU performance in ``resume training'' mode compared to a complete training session.}
  \label{tab:warmrestart}
\end{table*}
\fyTodo{Insert table, significancy testing against full learning condition, for each domain}

Considerations, \fyTodo{To be completed}:

\begin{itemize}
\item even when trained from entirely scratch, very few systems are able to take advantage of the additional data for the 6 initial domains - this is observed on the averaged scores in Table~\ref{tab:warmrestart} with hardly surpass those in Table~\ref{tab:performance}
\item restart is computationally cheaper (\fyTodo{how much cheaper here ?}) but underperforms cold start for all systems, sometimes by a wide margin.
\item the loss is largest for the small domains - how about distance to \domain{news} ?
\end{itemize}
\fyTodo{Very close to fine tuning towards News, no ?}:

@@

In \cite{Britz17mixing}, several methods are considered which aim to ensure that domain information is actually used in a mix-domain system. Three alternatives are considered, using either domain classification (or domain normalization, via adversarial training) on source or target representations. There is no clear winner in either of their three language pairs considered, which only distinguish a limited number of domains. The same basic techniques are simultaneously at play in \cite{Zeng18multidomain,Su19exploring}: in this approach, the upper layers of the MT aimed to sort out domain specific information on the one hand, and domain-agnostic information on the other hand, using auxiliary classification tasks, hoping that the domain-specific part will capture specific peculiarities of a domain, while the domain-agnostic part will be useful across the board. These techniques are implemented in an attentional sequence-to -sequence architecture in \cite{Zeng18multidomain}, and in Transformers in \cite{Su19exploring}.

@@

\subsection{Formalizing multi-domain adaptation (MDA)}

In MDA, the typical training situation is to work with $k$ domains with $\mathcal{D}_k(x)$ the distribution of features $x \in \mathcal{X}$ for domain $k$. Given a labelling function $f \mathcal{X} \rightarrow{} \mathcal{Y}$, \cite{Mansour09domainadaptation} assumes $k$ hypotheses $h_k(x): \mathcal{X} \rightarrow{} \mathcal{Y}$ with an error smaller than $\epsilon$ when $x\sim \mathcal{D}_k$: $\sum_{x} L(h_k(x), f(y)) \mathcal{D}_k(x) < \epsilon_k$.  The target distribution is a convex combination of $\{\mathcal{D}_k\}$: $\mathcal{D}_T(x) = \sum_k \lambda_k \mathcal{D}_k(x)$. \cite{Mansour09domainadaptation} derives generalization bounds for \textsl{combined hypotheses}, ie.\ hypotheses for which each prediction $h(x)$ is a linear combination of domain specific hypotheses $h(x_k)$. In this setting, one can study:
\begin{itemize}
\item generalization bounds when $\mathcal{D}_T(x)$ is fixed in advance, or worst case bounds valid for any mixture target distribution; the optimal solution has the form $h_{z,\eta}(x) = \sum_k \frac{z_kD_k(x) + U(x)/\gamma}{\sum_{k'} z_kD_k(x) + \eta U(x)/l}$ and is termed the \emph{distribution weighted combined rule}.
\item diverging from this simple case, subsequent work in \cite{Mansour09multiple} generalizes this bound to the case where $\mathcal{D}_T$ is not a mixture of existing domains (in that case we will find a mixture that is close in the Renyì-divergence sense ); where $\mathcal{D}_k$ are unknown and estimated from the data; or when the labelling function is not the same across domains. More recent work study the case where the labelling function is stochastic, meaning that domains are defined by joint ($\mathcal{D}_k(x,y)$) rather than marginal distributions \cite{Hoffman18algorithms}, and provides an algorithm to compute the optimal weights for the combined rule based on estimates of the joint distributions.

\item finite-sample bounds for the case where the target domain is known (\emph{multi-source single target adaptation} where we adapt from multiple sources studied in \cite{Cortes19AdaptationBO,Wen19domain}) - the issue is to optimize the selection / weighting of training data
\item finite-sample bounds and algorithm for unsupervised MDA
  % (http://papers.nips.cc/paper/8075-adversarial-multiple-source-domain-adaptation.pdf), test data are unlabeled;
  This setting is also the focus of (Domain Adaptation from Multiple Sources via Auxiliary Classifiers)
  %https://dl.acm.org/doi/pdf/10.1145/1553374.1553411 
\end{itemize}
